Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-06-20 papers/paper-eccentricity/paper-eccentricity.tex
First version of Intro done, minor additions

The SMBH binary merging process and its dependence on eccentricity has been extensively studied using collisionsless merger simulations \citep[e.g.][]{Berentzen2009,Vasiliev2015,gualandris2017,gualandris2022}. In a recent study \citet{nasim2020} have argued that the scatter in SMBH binary eccentricity observed in gas-free merger simulations is in fact an artefact of poor phase space
discretisation, and that in the real Universe where SMBH masses are far greater than stellar masses $(M_\bullet \gg m_\star)$, SMBH binary eccentricity is a reliably predictable quantity.

>>>>

The SMBH binary merging process and its dependence on eccentricity and resolution has been extensively studied using collisionsless merger simulations \citep[e.g.][]{Berentzen2009,Vasiliev2015,Bortolas2016,gualandris2017,gualandris2022}. Specifically, in a recent study \citet{nasim2020} have argued that the scatter in SMBH binary eccentricity observed in gas-free merger simulations is in fact an artefact of poor phase space
discretisation, and that in the real Universe where SMBH masses are far greater than stellar masses $(M_\bullet \gg m_\star)$, SMBH binary eccentricity is a reliably predictable quantity.
